Analyses

### 2021-11-19 src/analysis/analyses.Rmd
add analyses'

```{r "scale", fig.align="center", fig.height=8, fig.width=8}
source(here("src/analysis/explorative_cfa.R"))

@@

## IRT Analyse
```{r "irt-code", fig.align="center", fig.height=8, fig.width=12, results="hide", fig.show='hide'}
source(here("src/analysis/IRT.R"))

@@

>>>>

### CFA
```{r "scale", fig.align="center", fig.height=8, fig.width=8}
source(here("src/analysis/explorative_cfa.R"))

@@

### Additive scale
```{r "addative", fig.align="center", fig.height=8, fig.width=12, results="hide", fig.show='hide'}
source(here("src/analysis/additive-scale.R"))

kbl(add1, booktabs =T, caption = "Confirmatory Factor Analysis") %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = F, fixed_thead = T, position = "center") %>%
  column_spec(1, width = "10cm") %>%
  column_spec(2, width = "3cm")

add2
```

### Wüttke et al. Approach
```{r "wuttke", fig.align="center", fig.height=8, fig.width=12, results="hide", fig.show='hide'}
source(here("src/analysis/wuttke-approach.R"))

kbl(wa1, booktabs =T, caption = "Confirmatory Factor Analysis") %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = F, fixed_thead = T, position = "center") %>%
  column_spec(1, width = "10cm") %>%
  column_spec(2, width = "3cm")

wa2
```

### IRT Analyse
```{r "irt-code", fig.align="center", fig.height=8, fig.width=12, results="hide", fig.show='hide'}
source(here("src/analysis/IRT.R"))

@@

## Explanatory Power: Predicting Populist Vote
```{r "predict-vote-1", fig.align="center", fig.height=8, fig.width=8}
source(here("src/analysis/predict-pop-vote-scales.R"))
exp
```

```{r "predict-vote-2", fig.align="center", fig.height=8, fig.width=8}
source(here("src/analysis/predict-pop-vote-items.R"))
exp
```
